### 2020-06-10 writeup/proofs_sec3.tex
app wip

@@

%\section{Missing Details of Problem Formulation}

>>>>

\textbf{Organizations.}
The appendix is organized as follows.
In Section \ref{app_proof_sec3}, we describe an extended background and a further reivew of related work.
In Section \ref{app_proof_main_thm}, we present the analysis of the bias-variance tradeoff for the case of two tasks.
In Section \ref{app_iso_cov}, we illustrate the above analysis in simplified settings including the isotropic model and covariate shifted settings without model distance.
In Section \ref{app_proof_many_tasks}, we extend our analysis to many tasks with the same features.
In Section \ref{sec_maintools}, we prove the bias and variance bounds used in the analysis.
Finally in Section \ref{app_experiments}, we fill in the missing details of our experiments.

@@

We restate our linear regression setting, in particular the moment assumption required by our random matrix model.
We then derive a closed-form solution of the multi-task estimator that is defined in Section \ref{sec_prelim}.
Finally, we describe further related work that is covered in the main text.
%\section{Missing Details of Problem Formulation}
